---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

##Instructions of the usage of rBS2ndStructure

This package provides thermal stable RNA 2ndary structures predicted on full length transcripts mm10 and hg19. The RNA secondary structures are used to filter the bisulfite sequening sites that potentially have incomplete bisulfite conversion on thermal stable RNA secondary structures.

- First, install the package in R

```{r}
devtools::install_github("ZhenWei10/rBS2ndStructure")
library(rBS2ndStructure)
```

- Then, you may check and use the following data in the package.

```{r}
library(GenomicRanges)

?rBS2ndStructure::Struc_hg19

?rBS2ndStructure::Struc_mm10
```


- You could try to filter the sites overlapped with RNA secondary structure with the provided function.

```{r}
rBS_gr = GRanges(seqnames = rBS_df$`#SeqID`, strand = rBS_df$refStrand, ranges = IRanges(start = rBS_df$refPos, width = 1))
rBS_gr$mcols = p.adjust(rBS_df$`p-value_mState`,method = "BH") < .05
rBS_gr_filtered <- rBS_2ndStructure_Filter(rBS_gr,"hg19")
```

